Investigating the Safety of Different Toronto Neighbourhoods in 2011 Based on The Number of Crimes Reported

### 2024-09-26 paper/paper.qmd
References Updated

This paper uses @citeR and @rohan.

>>>>

This paper was created using statistical programming language R (@citeR) and was guided by (@rohan). Packages tidyverse (@citeTidyverse), knitr (@citeKnitr), ggplot2 (@citeGgplot2), and tibble (@citeTibble) were used as part of the code. The basis of the code was adapted from the book "Telling Stories with Data" (@tellingstorieswithdata).
